---
title       : Stopping Distance Prediction App
subtitle    : 
author      : Aaditya Bhat
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

The app uses 'cars' dataset in R. It fits Linear Regression model to the data, treating distance as response and speed as regressor.



```{r, echo = FALSE}
data(cars)
```

```{r}
head(cars)
```

---

## Plotting speed and dist

```{r}
plot(cars)
```

---

## Linear Regression 

As speed and distance have a positive correlation, a linear regression will be a good fit for the data. When speed = 0 mph, dist = 0. Hence we do not calculate the intercept in the model. 
```{r, fig.height= 4, fig.width= 4}
model <- lm(dist~speed -1, data = cars)
plot(cars)
abline(model)
```

---
## Summary of the fitted model

```{r, echo = FALSE}
summary(model)
```

